---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)

# Import packages
library(pins)
library(dplyr)
library(learnr)
library(gradethis)

# Pull data
board_register("https://raw.githubusercontent.com/predictcrypto/pins/master/","hitBTC_orderbooks_github")
# Only use the latest 1,000 rows (feel free to remove this)
hitBTC <- head(pin_get("hitBTC_orderbooks_github", "hitBTC_orderbooks_github"),1000)

# Sort by latest data
hitBTC <- arrange(hitBTC, desc(date_time_utc))

# Setting for coding boxes
tutorial_options(exercise.cap = "Execute Your R Code Below", exercise.checker = gradethis::grade_learnr)

# Convert the ask price to numeric
hitBTC$ask_1_price <- as.numeric(hitBTC$ask_1_price)
```

## First Example Topic

### Exercise with Hint

You can create guided examples with coded exercises! Try using the box below to return the first 5 rows of data using the function `head()` on the `hitBTC` object. Click on the "Hint" button if you need help.

```{r firstExercise, exercise=TRUE, exercise.eval=TRUE}
hitBTC
```

```{r firstExercise-hint}
head(hitBTC)
```

```{r firstExercise-solution}
head(hitBTC)
```

### Quiz

You can even include quiz questions throughout the document. Do your best to answer the question below, or ask for a `Hint` by clicking on the button.

**What is the latest price for the cryptocurrency with the `symbol` equal to "BTC"?**

```{r btc-price, exercise=TRUE, exercise.eval=TRUE}
hitBTC
```

```{r btc-price-hint}
select(arrange(filter(hitBTC, symbol=='BTC'), desc(date_time_utc)), symbol, ask_1_price)
```

```{r quiz-btc}
quiz(
  question('What is the latest price for the cryptocurrency with the `symbol` equal to "BTC"?',
    answer("11432.78"),
    answer("1914.82"),
    answer("8594.12"),
    answer(toString(head(select(arrange(filter(hitBTC, symbol=='BTC'), desc(date_time_utc)),ask_1_price),1))[1], correct = TRUE)
  )
)
```

## Second Example Topic

Try one more question. Can you find the value of `symbol` for the cryptocurrency with the lowest `ask_1_price` in the `hitBTC` dataset?

```{r lowest-price, exercise=TRUE, exercise.eval=TRUE}
hitBTC
```

```{r lowest-price-hint}
hitBTC[which.min(hitBTC$ask_1_price),]$symbol
```

```{r lowest-price-solution}
hitBTC[which.min(hitBTC$ask_1_price),]$symbol
```


```{r quiz-lowest-price}
quiz(
  question('Which cryptocurrency has the lowest value of "ask", for the entire dataset?',
    answer("EOS"),
    answer("BTC"),
    answer(toString(hitBTC[which.min(hitBTC$ask_1_price),]$symbol), correct = TRUE),
    answer("ETH")
  )
)
```
